---
title: "31858336 - Homework 3"
author: "31858336"
output: html_document
---

Please read all instructions carefully.  Fill in all fields above (Espicially your student number) and remove square brackets. To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with Chinese characters.
Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevant output. Do not delete anything below these instructions.  Thank you! 



**Question 1A:**
```{r Question 1A}
#TRAIN AND ESTIMATE model1A (WITHOUT EXPENDITURE) HERE
#clean up everything first
rm(list = ls())
gc()

#read the data
rawData = read.csv("Student Data 6.csv")

#estimate function
rmse = function(model){
  mean((predict(model,validationData) - (validationData$card))^2)^0.5
}

#Model A training
#try to get some info about interactions
library(earth)

#training models
set.seed(1)

#filter out expenditure
modelAData = subset(rawData,select = -expenditure)
#split the data
isTraining = runif(nrow(modelAData)) < 0.8
trainingData = subset(modelAData, isTraining)
validationData = subset(modelAData, !isTraining)



#descriptive analysis to get insights first
modelA1 = lm(card~., data = modelAData)
anova(modelA1)
#looks like besides "age" and "months", other factos matter

#to verify my guess, use BIC
library(leaps)
basicSubset = regsubsets(card~.,data = modelAData)
basicSummary = summary(basicSubset)
bestBIC = which.min(basicSummary$bic)
coef(basicSubset,bestBIC) #my guess is fair

#predictive analysis
#linear models
modelA2 = lm(card ~ . -age-months,data = modelAData)
modelA3 = lm(card~(.-age-months)^2, data = modelAData)

#further adjust based on anova
anova(modelA2)
modelA4 = lm(card ~ reports + income + share + owner + active, data = modelAData)

#MARS
modelA4 = earth(card ~., data = modelAData)
modelA5 = earth(card~.,  data = modelAData, degree = 2, thres = 0)
modelA6 = earth(card~.,  data = modelAData, degree = 2, thres = 0.01)
modelA7 = earth(card~.,  data = modelAData, degree = 2, thres = 0.1)

plotmo(modelA4)
plotmo(modelA5)

#apply some interactions
modelA6 = earth(card ~ reports + income + share + owner + active + share*reports + income*share + share*active, data = modelAData, thres = 0)
modelA7 = earth(card ~ reports + income + share + owner + active + share*reports + income*share + share*active, data = modelAData, thres = 0.01)
modelA8 = earth(card ~ reports + income + share + owner + active + share*reports + income*share + share*active, data = modelAData, thres = 0.1)

#random forest
library(randomForest)
modelA9 = randomForest(card ~. , data = modelAData)
modelA10 = randomForest(card ~.-age-months, data = modelAData)
modelA11 = randomForest(card ~ reports + income + share + owner + active, data = modelAData)
modelA12 = randomForest(card ~.^2, data = modelAData)
modelA13 = randomForest(card ~ (.-age-months)^2, data = modelAData)
rmse(modelA12)

#cross validation test with 5-folds
nFold = 5
#Step 1: Randomly choose which fold each row is in
set.seed(1)
valNum = floor(runif(nrow(modelAData))*nFold)+1
#all models
modelList = list(modelA1,modelA2,modelA3,modelA4,modelA5,modelA6,modelA7,modelA8,modelA9,modelA10,modelA11,modelA12,modelA13)
#all models storage
modelPerformance = matrix(NA,nFold,length(modelList)+1) #plus 1 to store the min value model

for(fold in 1:nFold){
    #Step 2i: Get the training and validation data for this fold
		trainingData = subset(modelAData,valNum!=fold)
		validationData = subset(modelAData,valNum==fold)
		
	  #Step 2ii: loop every models in this fold
		for(m in 1:length(modelList)){
		  model = modelList[[m]] 
		  performance = rmse(model)
		  modelPerformance[fold,m] = performance
		}
    
	  #find the best model in this fold
		modelPerformance[fold,length(modelList)+1] = which.min(modelPerformance[fold,c(1:length(modelList))])
}

bestModel = sort(modelPerformance[,length(modelList) + 1],decreasing = TRUE)[1]

```



**Question 1B:**
```{r Question 1B}
#TRAIN AND ESTIMATE model1B (WITH EXPENDITURES) HERE
```


```{r}
#Fill in your student number in the line below to generate the RData file for submission. DO NOT CHANGE ANYTHING ELSE ABOUT THE CODE BELOW.
studentNum = 31848336 

#This reduces the file size in some cases fringe cases
model1A$cv.list = NULL
model1A$cv.oof.fit.tab = NULL
model1A$varmod = NULL

model1B$cv.list = NULL
model1B$cv.oof.fit.tab = NULL
model1B$varmod = NULL

save(model1A, model1B, file = paste0(studentNum,'.Rdata'))

#The following code checks if you generated the models correctly.  Run it, and if you see 'looks good!' pop up twice then your Rdata file is ready. Do not alter it any way - not even to change the variable names.  If not, please correct, or contact the TAs for help 
load(paste0(studentNum,'.Rdata'))
rightType = class(model1A)=='earth'|class(model1A)=='lm'
rightType2 = class(model1B)=='earth'|class(model1B)=='lm'
if(class(model1A)=='earth'){
	noExpend = grepl('[^-]expenditure',paste(rownames(model1A$coefficients),collapse=''))
}  else {
	noExpend = grepl('[^-]expenditure',paste(names(model1A$coefficients),collapse=''))
}

if(rightType&rightType2&noExpend){ 
	print('Looks Good!')
} else {
	print('Mistake - Check that you are saving lm and earth models, and that expenditure is not in the first model')
}


checkModel(model1A)
checkModel(model1B)

```